Suplementary Material 3: Run Simulations on the Last Birth Omited Data

### 2023-04-10 S3_run_simulations_EE_not_last.Rmd
updated RAM usage info

The memory (RAM) and usage is quite high for simulations. Below there are some information about the RAM  usages per  CPU of simulations on Estonian data w/o last birth. The total number of CPUs used for running these simulations was 61.

Memory usage per CPU:

  * base model: about 15GB (dumped cores have a size range 12-23GB)

@@

>>>>

The memory (RAM) and usage is quite high for simulations. Below there are some information about the RAM  usages per  CPU of simulations on Estonian data w/o last birth. The total number of CPUs used for running these simulations was 51. RAM usage varied between models but stayed around 18 GB per CPU core (dumped cores had a size range from 12 to 23GB).

@@

Its suggested to use a linux computing cluster to run the simulation scenarios one by one (using *run_simulation_EE_not_last.R*) rather than running the for loop below. Example of a bash command > **Rscript run_simulation_EE_not_last.R --model H --cores 51**. The model indicates the scenario to be run.
